R Notebook

### 2021-06-11 Paper_Figure_code.Rmd
code_for_figures

melt_merge_melt_silico_1700 <- merge_melt_silico_1700 %>%
    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

@@

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + # 不要背景
    theme(axis.title.x=element_blank(), # 去掉 title
          axis.ticks.x=element_blank(), # 去掉x 轴
          axis.title.y=element_blank(), # 去掉 y 轴
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("1700 simulated RNA-seq data sets (ID: 6)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

@@

melt_merge_TCGA_LUAD_Lymphocytes_RNAseq <- merge_TCGA_LUAD_Lymphocytes_RNAseq %>%
    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

@@

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + # 不要背景
    theme(axis.title.x=element_blank(), # 去掉 title
          axis.ticks.x=element_blank(), # 去掉x 轴
          axis.title.y=element_blank(), # 去掉 y 轴
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("H&E stained (ID: 4)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

@@

melt_merge_Melanoma_GSE72056 <- merge_Melanoma_GSE72056 %>%
    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

@@

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + # 不要背景
    theme(axis.title.x=element_blank(), # 去掉 title
          axis.ticks.x=element_blank(), # 去掉x 轴
          axis.title.y=element_blank(), # 去掉 y 轴
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("19 reconstructed non-malignant melanoma (ID: 9)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

@@

melt_merge_Melanoma_GSE93722 <- merge_Melanoma_GSE93722 %>%
    mutate(text = case_when(  # 一定要 get 到 case_when() 函数奥秘
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), # round() 只保留两位小数
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

@@

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + # 不要背景
    theme(axis.title.x=element_blank(), # 去掉 title
          axis.ticks.x=element_blank(), # 去掉x 轴
          axis.title.y=element_blank(), # 去掉 y 轴
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), # 调整x轴文字，字体加粗
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("4 malignant melanoma (ID: 8)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

>>>>

melt_merge_melt_silico_1700 <- merge_melt_silico_1700 %>%
    mutate(text = case_when(  
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), 
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

@@

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + 
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), 
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("1700 simulated RNA-seq data sets (ID: 6)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

@@

melt_merge_TCGA_LUAD_Lymphocytes_RNAseq <- merge_TCGA_LUAD_Lymphocytes_RNAseq %>%
    mutate(text = case_when(  
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), 
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

@@

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + 
    theme(axis.title.x=element_blank(), 
          axis.ticks.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), 
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("H&E stained (ID: 4)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

@@

melt_merge_Melanoma_GSE72056 <- merge_Melanoma_GSE72056 %>%
    mutate(text = case_when(  
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), 
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

@@

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + 
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"), 
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("19 reconstructed non-malignant melanoma (ID: 9)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))

@@

melt_merge_Melanoma_GSE93722 <- merge_Melanoma_GSE93722 %>%
    mutate(text = case_when(  
        is.na(value.1) & is.na(value) ~ paste("NA", "\n"),
        is.na(value.1) & (value == 0) ~ paste(value, "\n"),
        value.1 >= 0.05 ~ paste(value, "\n"),
        value.1 >= 0.01& value.1 < 0.05  ~ paste(value, "\n*"), 
        value.1 >= 0.001 & value.1 < 0.01 ~ paste(value, "\n**"),
        value.1 < 0.001 ~ paste(value, "\n***")))

@@

    geom_text(aes(label=text),col ="black",size = 5) +
    theme_minimal() + 
    theme(axis.title.x=element_blank(), 
          axis.ticks.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.title=element_text(size = 14),
          legend.text=element_text(size = 14),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14, colour = "black"),
          axis.text.y = element_text(size = 14, colour = "black")) + labs(fill =paste0("Correlation")) + ggtitle("4 malignant melanoma (ID: 8)") + theme(plot.title = element_text(hjust = 0.5, size = 16 ))
